Classless Java: Tuning Java Interfaces

### 2015-12-08 paper/sections/Translation.tex
S5.4 revised

\subsection{Results}
To formally characterize the behaviour of our annotation, and the two level of guarantees that we offer, we provide some notations and two theorems:
\begin{itemize}
\item We denote with $\C^{\II}$ the name of an interface.
\item An interface table
IT is OK if under such interface table, all interfaces are OK.
\item Since interface tables are just represented as sequences of interfaces we write IT = $\II$ IT' to select a specific interface in a table.
\item IT contains an heir of $\C$ if there is an interface that extends it, or a \Q@new@ that instantiate it.
\end{itemize}

@@

Informally, the theorems mean that for a client program that
typechecks before a translation is applied, if the annotated type has
no subtypes, and no objects of that type are created, then type safety
is guaranteed after the successful translation.

The second
step of \mixin, namely what $\weakAnn$ does in the formalization, is
guaranteed to be type-safe for the three kinds of coherence by the $\weakAnn$  tuning theorem.
\mixin
tuning is more interesting: Since \mixin does not guarantee heir
coherence, we exclude explicitly the presence of heirs. In this way
\mixin tuning guarantees only self and client coherence. The formal
theorem proofs are available in the supplementary materials.%~\ref{subsec:lemma1},~\ref{subsec:lemma2} and~\ref{subsec:theorem}.\\

>>>>

\subsection{Results}
To formally characterize the behaviour of our annotation and the two levels of guarantees that we offer, we provide some notations and two theorems:
\begin{itemize}
\item We denote with $\C^{\II}$ the name of an interface.
\item An interface table
IT is OK if under such interface table, all interfaces are OK.
\item Since interface tables are just represented as sequences of interfaces we write IT = $\II$ IT' to select a specific interface in a table.
\item IT contains an heir of $\C$ if there is an interface that extends it, or a \Q@new@ that instantiate it.
\end{itemize}

@@

Informally, the theorems mean that for a client program that
typechecks before the translation is applied, if the annotated type has
no subtypes, and no objects of that type are created, then type safety
is guaranteed after the successful translation.

The second
step of \mixin, namely what $\weakAnn$ does in the formalization, is
guaranteed to be type-safe for the three kinds of coherence by the $\weakAnn$  tuning theorem.
\mixin
tuning is more interesting: since \mixin does not guarantee heir
coherence, we explicitly exclude the presence of heirs. In this way
\mixin tuning guarantees only self and client coherence. The formal
theorem proofs are available in the supplementary materials.%~\ref{subsec:lemma1},~\ref{subsec:lemma2} and~\ref{subsec:theorem}.\\
